Untitled

### 2017-07-15 PaperCode.Rmd
DistribCompare upgrade
I have changed Distrib compare to be able to create bootstrapps of type A and B purchases only

setwd(basewd)
#Boostrap each LAD
elementnames <- sub("DATA", "", ls(pattern = "DATA"))

if(file.exists("BootStrapRES.rds")){
 #this sectio of code loads the old list and appends the new LADs

  BootStrapRES<- readRDS("BootStrapRES.rds")
  newLADsnames <- sub("DATA", "", ls(pattern = "DATA")) %>% 
  .[!(. %in% names(BootStrapRES))] 
  newLADs <- paste0(newLADsnames, "DATA")

    #only bootstrap if there is something to add.
    if(length(newLADsnames)>0){
       newLADsBoot <- newLADs  %>% map(~{print(.x)
          DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})  
          names(newLADsBoot) <- newLADsnames
          BootStrapRES <- c(BootStrapRES, newLADsBoot)
     }

 #re-roder the whole lot to be alphabetical
 BootStrapRES <- BootStrapRES [order(names(BootStrapRES))]

}else{
  #If the list is not found it bootstrapps all the LADs at once, beware this can take a long time

  BootStrapRES <- ls(pattern = "DATA") %>% map(~{print(.x)
  DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})
  #Give the resulting list the name of each LAD
  names(BootStrapRES)<- elementnames

}
#SAve the file or updated file with the additional elements
saveRDS(BootStrapRES, file = "BootStrapRES.rds")

@@

test <- BootStrapRES$Ceredigion
#look at specific data
BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")

>>>>

setwd(basewd)

#load full data
BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")

#Include only full price standard purchases
BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")

#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

@@

test <- BootStrapRES$Ceredigion
#look at specific data
BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
